Singapore's Public Housing Affordability

### 2023-11-14 datastory.qmd
Weekly Update

```{r, out.height= "200px",out.width="800px",echo=FALSE,eval=TRUE, fig.align='center'}
knitr::include_graphics("src/images/HDB-flat-after-divorce.jpg")
```
## Is Public Housing in Singapore Affordable for the Average Singaporean?

@@

According to Kumar (2022),
</p>

```{r, out.height= "200px",out.width="800px",echo=FALSE,eval=TRUE, fig.align='center', fig.cap="Estimation of Average Salary Per Spouse (Kumar, 2022)"}
knitr::include_graphics("docs/images/dreamhome.png")
```

@@

>>>>

![](src/images/HDB-flat-after-divorce.jpg){width="698"}

## Is Public Housing Affordable for Singaporeans?

@@

According to Kumar (2022),

![](docs/images/dreamhome.png){width="698"}

@@

<iframe height="400" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/example/"></iframe>
